{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-10-31 main.tex
Increment

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}	
	Functional Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is gaining more attention as researchers from different fields collect data that is functional in nature. This data can often be processed by classical statistical methods, but only FDA allows extracting information given by the smoothness of the underlying process (cf. \cite{levitin_introduction_2007}).
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).\\
	 To motivate scalar-on-function regression, consider the case of a data set containing a scalar response and observations of an underlying continuous process. In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
	 The focus of this paper is to introduce Functional Linear Regression (FLR) in a scalar-on-function setting. We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:  {\color{red} (I don't set up any interval for s here we might do later...)}
	 \begin{equation}
	 	Y_{i} = \beta_{0} + \int{X_{i}(s)\beta(s)ds} + \epsilon_{i},
	 	\qquad i = 1, ..., n
	 \end{equation}
	 where the $X_{i}$ are observations of a random function $X$, $Y_i$ are realizations of the response variable and $\beta(s)$ is the coefficient function. The distinct feature of this framework is that the regressor is a function, which necessitates a different approach to estimation. As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(s)$ for prediction. For instance, fluctuation in $X$ at a point $s_0$ will not have any effect on $Y$ if $\beta(s_0)$ = 0. \\
	 Estimation of $\beta(s)$ is inherently an infinite dimensional problem. In Section 2, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using a concept called truncated basis expansion. The results of the Monte-Carlo simulation regarding these three different methods are reported in Section 3. Finally, in Section 4, we test the prediction of FLR in a real world setting. {\color{red} (We may put some simple descriptions of results about each of MC and Application)}

@@

	\begin{itemize}
		\item Explain problem of naively extending multivariate linear regression to infinite dimensions
	\end{itemize}
	Assuming a data generating process of the form:
	\begin{equation}
     Y =  \int \beta(s)X(s) \,dt \ +\epsilon
    \end{equation}
    it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because of the infinite dimensionality of the underlying objects. Define therefore
    \begin{equation}
  	c_{X}(t,s) = E[X(t)X(s)],\: c_{XY}(t) = E[X(t)Y], 
    \end{equation}
   Under the assumption that $X$ is independent from $\epsilon$ we obtain
   \begin{equation}
     c_{XY}(t) = E[X(t)\int \beta(t)X(s) \,dt \ +\epsilon
   \end{equation}
    \begin{equation}
     c_{XY}(t) = \int \beta(s)\,dt \: E[X(s)X(t)| X] + E[\epsilon |X]
  	\end{equation}
   	\begin{equation}
    	c_{XY}(t) = \int c_{X}(t,s) \beta(s) \,ds 
   \end{equation}

@@

   If we approximate the scalar-on-functional regression as
  	\begin{equation}
     Y_i = \sum_{i = 1}^{n} \beta(t_{i})X_1(t_{i}) + \epsilon_{i}
    \end{equation}, it becomes clear that if $t_{i}$ is close to $t_{i'}$, $X_{i}(t_{i})$ is close to $X_{i}(t_{i'})$ there will be vectors $X_{i}$ that are highly correlated and thus lead to large variances.

>>>>

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}	
	Functional Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is gaining more attention as researchers from different fields collect data that is functional in nature. This data can often be processed by classical statistical methods, but only FDA allows extracting information given by the smoothness of the underlying process (cf. \cite{levitin_introduction_2007}).
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).\\
	 To motivate scalar-on-function regression, consider the case of a data set containing a scalar response and observations of an underlying continuous process. In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
	 The focus of this paper is to introduce Functional Linear Regression (FLR) in a scalar-on-function setting. We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:  {\color{red} (I don't set up any interval for s here we might do later...)}
	 \begin{equation}
	 	Y_{i} = \beta_{0} + \int{X_{i}(s)\beta(s)ds} + \epsilon_{i},
	 	\qquad i = 1, ..., n
	 \end{equation}
	 where the $X_{i}$ are realizations of a random function $\mathbf{X}$, $Y_i$ are the corresponding realizations of the response variable and $\beta(s)$ is the coefficient function. The distinct feature of this framework is that the regressor is a function, which necessitates a different approach to estimation. As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(s)$ for prediction. For instance, fluctuation in $X_i(s)$ at a point $s_0$ will not have any effect on $Y_i$ if $\beta(s_0)$ = 0. \\
	 Estimation of $\beta(s)$ is inherently an infinite dimensional problem. In Section 2, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using a concept called truncated basis expansion. The results of the Monte-Carlo simulation regarding these three different methods are reported in Section 3. Finally, in Section 4, we test the prediction of FLR in a real world setting. {\color{red} (We may put some simple descriptions of results about each of MC and Application)}

@@

	\begin{itemize}
		\item Explain problem of naively extending multivariate linear regression to infinite dimensions
	\end{itemize}
	Assuming a data generating process of the form:
	\begin{equation}
     Y =  \int \beta(s)X(s) \,dt \ +\epsilon
    \end{equation}
    it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because of the infinite dimensionality of the underlying objects. Define therefore
    \begin{equation}
  	c_{\mathbf{X}}(t,s) = E[\mathbf{X}(t)\mathbf{X}(s)],\: c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\mathbf{Y}], 
    \end{equation}
   Under the assumption that $X$ is independent from $\epsilon$ we obtain
   \begin{equation}
     c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\int \beta(t)\mathbf{X}(s) \,ds \ +\epsilon]
   \end{equation}
    \begin{equation}
     c_{\mathbf{X}\mathbf{Y}}(t) = E[\int \beta(s) \: \mathbf{X}(s)\mathbf{X}(t) \, ds \: | \: X]  + E[\epsilon |\mathbf{X}]
  	\end{equation}
   	\begin{equation}
    	c_{\mathbf{X}\mathbf{Y}}(t) = \int c_{\mathbf{X}}(t,s) \beta(s) \,ds
   \end{equation}

@@

   If we approximate the scalar-on-functional regression as
  	\begin{equation}
     Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{j}
    \end{equation}, it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$ there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances. {\color{red} isn't something missing here? Like "and employ standard multivariate linear regression"}
